Between-dataset comparisons

### 2019-11-12 analysis/reports/compare_datasets.Rmd
change memory strategy

---
title: "Between-dataset comparisons"
output: 
  github_document
params:
---

@@

datasets <- c("bbs", "fia", "gentry", "mcdb", "misc_abund_short", "portal_plants")

for(i in 1:6) {

@@

all_statevars <- all_statevars %>%
  filter(!singletons) %>%
  mutate(in_bbs = between(s0, all_extremes$min_s0[1], all_extremes$max_s0[1]) + between(n0, all_extremes$min_n0[1], all_extremes$max_n0[1]) == 2,
         in_fia = between(s0, all_extremes$min_s0[3], all_extremes$max_s0[3]) + between(n0, all_extremes$min_n0[3], all_extremes$max_n0[3]) == 2,
         in_gentry = between(s0, all_extremes$min_s0[5], all_extremes$max_s0[5]) + between(n0, all_extremes$min_n0[5], all_extremes$max_n0[5]) == 2,
         in_mcdb = between(s0, all_extremes$min_s0[7], all_extremes$max_s0[7]) + between(n0, all_extremes$min_n0[7], all_extremes$max_n0[7]) == 2,
         in_misc = between(s0, all_extremes$min_s0[9], all_extremes$max_s0[9]) + between(n0, all_extremes$min_n0[9], all_extremes$max_n0[9]) == 2,
         in_portal = between(s0, all_extremes$min_s0[11], all_extremes$max_s0[11]) + between(n0, all_extremes$min_n0[11], all_extremes$max_n0[11]) == 2) %>%
  mutate(total_in = in_bbs + in_fia + in_gentry + in_mcdb + in_misc + in_portal)

@@

>>>>

---
title: "Between-dataset comparisons"
output: 
  github_document
---

@@

# datasets <- c("bbs", "fia", "gentry", "mcdb", "misc_abund_short", "portal_plants")

datasets <- c("fia", "gentry", "mcdb", "misc_abund_short", "portal_plants")

for(i in 1:length(datasets)) {

@@

all_statevars <- all_statevars %>%
  filter(!singletons) %>%
  mutate(
    # in_bbs = between(s0, filter(all_extremes, dat == "bbs", singletons == F)$min_s0[1], filter(all_extremes, dat == "bbs", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "bbs", singletons == F)$min_n0[1], filter(all_extremes, dat == "bbs", singletons == F)$max_n0[1]) == 2,
    in_fia = between(s0, filter(all_extremes, dat == "fia", singletons == F)$min_s0[1], filter(all_extremes, dat == "fia", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "fia", singletons == F)$min_n0[1], filter(all_extremes, dat == "fia", singletons == F)$max_n0[1]) == 2,
    in_gentry = between(s0, filter(all_extremes, dat == "gentry", singletons == F)$min_s0[1], filter(all_extremes, dat == "gentry", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "gentry", singletons == F)$min_n0[1], filter(all_extremes, dat == "gentry", singletons == F)$max_n0[1]) == 2,
    in_mcdb = between(s0, filter(all_extremes, dat == "mcdb", singletons == F)$max_s0[1], filter(all_extremes, dat == "mcdb", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "mcdb", singletons == F)$min_n0[1], filter(all_extremes, dat == "mcdb", singletons == F)$max_n0[1]) == 2,
    in_misc = between(s0, filter(all_extremes, dat == "misc_abund_short", singletons == F)$max_s0[1], filter(all_extremes, dat == "misc_abund_short", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "misc_abund_short", singletons == F)$min_n0[1], filter(all_extremes, dat == "misc_abund_short", singletons == F)$max_n0[1]) == 2,
    in_portal = between(s0, filter(all_extremes, dat == "portal_plants", singletons == F)$max_s0[1], filter(all_extremes, dat == "portal_plants", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "portal_plants", singletons == F)$min_n0[1], filter(all_extremes, dat == "portal_plants", singletons == F)$max_n0[1]) == 2
    ) %>%
  # mutate(total_in = in_bbs + in_fia + in_gentry + in_mcdb + in_misc + in_portal)
  mutate(total_in =in_fia + in_gentry + in_mcdb + in_misc + in_portal)

@@

```{r intersection plot}

intersection_plot <- ggplot(data = filter(all_statevars, singletons == FALSE, total_in > 1), aes(x = s0, y = n0, color = as.factor(total_in))) +
  geom_point(alpha = .2) +
  theme_bw() +
  scale_color_viridis_d(option = "plasma", end = .9)
intersection_plot
